---
title: "Assignment_9"
author: "Peyton Bailey"
date: "2022-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
```

## R Markdown
# For this report we will be looking at grad school admissions
This will give a glimpse of the data
```{r}
library(tidyverse)
library(skimr)
df <- read_csv("../Data/GradSchool_Admissions.csv")
 df1 <-  df %>% mutate(enrolled=case_when(admit == 1 ~ TRUE ,TRUE~FALSE))

 skim(df) 
 
 
```


Here is a data table you can filter the categories using a slider to further explore the data set




```{r}
 
 library(DT)
 
 
 datatable(df1, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T) )
```

___

## Plots 



#### GPA vs GRE





```{r,fig.align='center'}
plot1 <- df1 %>% ggplot(aes(x=gpa,y=gre,color=enrolled))+  geom_smooth(method = "lm",se=FALSE) 

library(plotly)
ggplotly(plot1)
```

#### GPA vs GRE by rank in the class


```{r,fig.align='center'}
plot2 <- df1 %>% ggplot(aes(y=gpa,x=gre,color=enrolled))+  geom_smooth(method = "lm", se = FALSE) +facet_wrap(~rank)

ggplotly(plot2)


```


##### This shows that those ranked 2nd got in the most

```{r}
plot3 <- df1 %>% ggplot(aes(x=rank,y=gpa))+ geom_point()+ facet_wrap(~enrolled)

ggplotly(plot3)
```







## models


model 1
```{r}

library(easystats)
library(kableExtra)
mod1 <- glm(df1,formula = enrolled ~ gpa * gre + rank, family = "binomial")
performance(mod1)

formula(mod1)

broom::tidy(mod1) %>% kable() %>% kable_classic(lightable_options = 'hover') %>% kable_material_dark()
```



model 2


```{r}
mod2 <- glm(df1,formula = enrolled ~ gpa * gre * rank, family = "binomial")

model_performance(mod2)
formula(mod2)
broom::tidy(mod2) %>% kable() %>% kable_classic(lightable_options = 'hover') %>% kable_material_dark()

```

comparing the models performance

```{r}
compare_performance(mod1,mod2,rank=TRUE)
```

## Predictions
Percent chance of getting enrolled based on GRE
```{r}

library(modelr)

modeldf <- add_predictions(df1,mod1,type="response") 

plot4 <-  modeldf %>% ggplot(aes(x=pred,y=gre))+ geom_smooth(se=FALSE)

ggplotly(plot4)

```




Percent chance of getting enrolled based on GPA

```{r}
plot5 <- modeldf %>% ggplot(aes(y=gpa,x=pred)) + geom_smooth(se=FALSE)
ggplotly(plot5)
```
***To access the link open in web browser***
[If your feeling down on your chances click HERE](file:///Users/Owner/Desktop/Data_Course_BAILEY/grad_school_motivation/Docs/index.html)
